Constant Rate Computational Fuzzy Extractors

### 2013-12-10 trunk/constantRate/ConstCompFuzzExt.tex
Reorganized and adding constant rate work

\ifnum\shownotes=1
\newcommand{\authnote}[2]{{\textcolor{red}{\textsf{#1 notes: }\textcolor{blue}{ #2}}\marginpar{\textcolor{red}{\textbf{!!!!!}}}}}
\else
\newcommand{\authnote}[2]{}
\fi
\newcommand{\bnote}[1]{{\authnote{Ben}{#1}}}
\newcommand{\lnote}[1]{{\authnote{Leo}{#1}}}
\newcommand{\xnote}[1]{{\authnote{Xianrui}{#1}}}

@@

\title{Computational Fuzzy Extractors}
\author{Benjamin Fuller 
\footnote{Email: {\tt bfuller@cs.bu.edu}.  Work done in part while the author was at MIT Lincoln Laboratory.}
~~~~~~~~Xianrui Meng\footnote{Email: {\tt xmeng@cs.bu.edu}.}~~~~~~~~~Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.} \\ Boston University}
%\author{}
\begin{document}
\maketitle

\begin{abstract} 
Fuzzy extractors derive strong keys from noisy sources.  Their
security is defined information-theoretically, which limits the length
of the derived key, sometimes making it too short to be useful. We ask
whether it is possible to obtain longer keys by considering
computational security, and show the following.

\begin{itemize}
\item\textbf{Negative Result:} Noise tolerance in fuzzy extractors is usually
achieved using an information reconciliation component called a ``secure
sketch.'' The security of this component, which directly affects the
length of the resulting key, is subject to lower bounds from coding
theory.  We show that, even when defined computationally, secure
sketches are still subject to lower bounds from coding theory. Specifically, we consider
two computational relaxations of the information-theoretic security requirement of secure sketches, using conditional HILL entropy and unpredictability entropy. For both cases we show  that computational secure sketches cannot outperform the best information-theoretic secure sketches in the case of high-entropy Hamming metric sources.

\item\textbf{Positive Result:} We show that the negative result can be overcome by
analyzing computational fuzzy extractors directly.  Namely, we show
how to build a computational fuzzy extractor whose output key length
equals the entropy of the source (this is impossible in the
information-theoretic setting). Our construction is based on the
hardness of the Learning with Errors (LWE) problem, and is secure when
the noisy source is uniform or symbol-fixing (that is, each dimension
is either uniform or fixed). As part of the security proof, we show a result of independent interest, namely
that the decision version of LWE is secure even when a small number of
dimensions has no error.
\end{itemize}
\textbf{Keywords} Fuzzy extractors, secure sketches, key derivation, Learning with Errors, error-correcting codes, computational entropy, randomness extractors.
\end{abstract}

\section{Introduction}\label{sec:introduction}

Authentication generally requires a secret drawn from some high-entropy source.  One of the primary building blocks for authentication is reliable key derivation.  Unfortunately, many sources that contain sufficient entropy to derive a key are  noisy, and provide similar, but not identical secret values at each reading (examples of such sources include biometrics~\cite{daugman2004}, human memory~\cite{zviran1993comparison}, pictorial passwords~\cite{brostoff2000passfaces}, measurements of capacitance~\cite{tuyls2006puf}, timing~\cite{suh2007physical}, motion~\cite{castelluccia2005shake},  quantum information~\cite{bennett1988privacy} etc.).

Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} achieve reliable key derivation from noisy sources~(see \cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy} for applications of fuzzy extractors).  The setting 
consists of  two algorithms: Generate (used once) and Reproduce (used subsequently).  The Generate ($\gen$) algorithm takes an input $w$ and produces a key $r$ and a public value $p$.  This information allows
the Reproduce ($\rep$) algorithm to reproduce $r$ given $p$ and some value $w'$ that is close to $w$ (according to some predefined metric, such as Hamming distance). 
Crucially for security,  knowledge of $p$ should not reveal $r$; that is, $r$ should be uniformly distributed conditioned on $p$.  This feature is needed because $p$ is not secret: for example, in a single-user setting (where the user wants to reproduce the key $r$ from a subsequent reading $w'$), it would be stored in the clear; and in a key agreement application~\cite{Boyen05secureremote} (where two parties have $w$ and $w'$, respectively), it would be transmitted between the parties.

Fuzzy extractors use ideas from information-reconciliation~\cite{bennett1988privacy} and are defined (traditionally) as information-theoretic objects.  The entropy loss of a fuzzy extractor is the difference between the entropy of $w$ and the length of the derived key $r$.  In the information-theoretic setting, some entropy loss is necessary as the value $p$ contains enough information to reproduce $r$ from any close value $w'$. 
A goal of fuzzy extractor constructions is to minimize the entropy loss, increasing the security of the resulting application.  Indeed, if the entropy loss is too high, the resulting secret key may be too short to be useful.

We ask whether it is possible to obtain longer keys by considering
computational, rather than information theoretic, security.

\paragraph {Our Negative Results}
We first study (in  \secref{sec:impossCompSecSketch}) whether it could be fruitful to relax the definition of the main building block of a fuzzy extractor, called a \emph{secure sketch}.  A secure sketch is a one-round information reconciliation protocol: it  produces a public value $s$ that allows recovery of $w$ from any close value $w'$.  The traditional secrecy requirement of a secure sketch is that $w$ has high min-entropy conditioned on $s$.  This allows the fuzzy extractor of~\cite{DBLP:journals/siamcomp/DodisORS08}  to form the key $r$ by applying a randomness extractor~\cite{nisan1993randomness} to $w$, because randomness extractors produce random strings from strings with conditional min-entropy. We call this the \emph{sketch-and-extract} construction.

The most natural relaxation of the min-entropy requirement of the secure sketch is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).  Under this definition, we could still use a randomness extractor to obtain $r$ from $w$, because it would yield a pseudorandom key.  Unfortunately, it is unlikely that such a relaxation will yield fruitful results: we prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.

Another possible relaxation is to require that the value $w$ is unpredictable conditioned on $s$. This definition would also allow the use of a randomness extractor to get a pseudorandom key, although it would have to be a special extractor---one that has  a reconstruction procedure (see \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).  Unfortunately, this relaxation is also unlikely to be fruitful:  we prove in \thref{thm:imp of unp entropy} that the unpredictability is at most $\log$ the size of the metric space minus $\log$ the volume of the ball of radius $t$.  For high-entropy sources of $w$ over the Hamming metric, this bound matches the best information-theoretic security sketches.

\paragraph {Our Positive Results}

Both of the above negative results arise because a secure sketch functions like a decoder of an error-correcting code.  To avoid them, we give up on building computational secure sketches and focus directly on the entropy loss in fuzzy extractors.  Our goal is to decrease the entropy loss in a fuzzy extractor by allowing the key $r$ to be pseudorandom conditioned on $p$.

By considering this computational secrecy requirement, we construct the first \emph{lossless} computational fuzzy extractors (\consref{cons:informal construction}), where the derived key $r$ is as long as the entropy of the source $w$. Our construction is for the Hamming metric and uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} used in prior work, but with two crucial differences.  First, the key $r$ is not extracted from $w$ like in the sketch-and-extract approach; rather $w$ ``encrypts'' $r$ in a way that is decryptable with the knowledge of some close $w'$ (this idea is similar to the way the code-offset construction is presented in 
\cite{JW99} as  a ``fuzzy commitment''). Our construction uses private randomness, which is allowed in the fuzzy extractor setting but not in noiseless randomness extraction.  Second, the code used is a random linear code, which allows us to use the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey} and derive a longer key $r$.

Specifically,  we use the  recent result of D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012}, which shows the hardness of decoding random linear codes when the error vector comes from the uniform distribution, with each coordinate ranging over a small interval. This allows us to use $w$ as the error vector, assuming it is uniform.  We also use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009},  which says that LWE has many hardcore bits, to hide $r$.

Because we use a random linear code,  our decoding is limited to reconciling a logarithmic number of differences.  Unfortunately, we  cannot utilize the results that improve the decoding radius through the use of trapdoors (such as \cite{regev2005LWE}), because in a fuzzy extractor, there is no secret storage place for the trapdoor. If improved decoding algorithms are obtained for random linear codes, they will improve error-tolerance of our construction.  Given the hardness of decoding random linear codes~\cite{berlekamp1978}, we do not expect significant improvement in the error-tolerance of our construction.

In \secref{sec:LWE block fixing sources}, we are able to relax the assumption that $w$ comes from the uniform distribution, and instead allow $w$ to come from a symbol-fixing source~\cite{KZ07} (each dimension is either uniform or fixed). This relaxation follows from our results about the hardness of LWE when samples have a fixed~(and adversarially known) error vector, which may be of independent interest~(\thref{thm:blockLWE}).

\paragraph{An Alternative Approach}  Computational extractors~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational} have the same goal of obtaining a pseudorandom key $r$ from a source $w$ in the setting without errors.  They can be constructed, for example, by applying a pseudorandom generator to the output of an information-theoretic extractor.  One way to build a computational \emph{fuzzy} extractor is by using a computational extractor instead  of the information-theoretic extractor in the sketch-and-extract construction of  \cite{DBLP:journals/siamcomp/DodisORS08}.   However, this approach is possible only if conditional min-entropy of $w$ conditioned on the sketch $s$ is high enough.  Furthermore, this approach does not allow the use of private randomness; private randomness is a crucial ingredient in our construction.
We compare the two approaches in \secref{sec:prg based comparison}.

\section{Preliminaries}
\label{sec:preliminaries}
For a random variable $X = X_1||...|| X_n$ where each $X_i$ is over some alphabet $\mathcal{Z}$, we denote by $X_{1,..., k} = X_1||...|| X_k$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$, 
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.  
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$. 
For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.  We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.
For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t(\cdot)|$ the size of a ball of radius $t$.  For the Hamming metric over $\mathcal{Z}^n$, $|B_t(\cdot)| = \sum_{i=0}^t {n \choose i} (|\mathcal{Z}|-1)^i $.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
Usually, we use bold letters for vectors or matrices, capitalized letters for random variables, and lowercase letters for elements in a vector or samples from a random variable.

@@

\textbf{Remark}  Fuzzy extractor definitions make no guarantee about \rep behavior when the distance between $w$ and $w'$ is larger than $t$.  In the information-theoretic setting this seemed inherent as the ``correct'' $R$ should be information-theoretically unknown conditioned on $P$.  However, in the computationally setting this is not true.  Looking ahead, in our construction $R$ is information-theoretically determined conditioned on $P$~(with high probability over the coins of \gen).  Our $\rep$ algorithm will never output an incorrect key~(with high probability over the coins of \gen) but may not terminate.  However, it is not clear this is the desired behavior.  For this reason, we leave the behavior of \rep ambiguous when $\dis(w, w')>t$.

\section{Impossibility of Computational Secure Sketches}
\label{sec:impossCompSecSketch}
In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational than information-theoretic entropy.  We consider two different notions for computational entropy, and for both of them show that corresponding secure sketches are subject to the same upper bounds as those for information-theoretic secure sketches. Thus, it seems that relaxing security of sketches from information-theoretic to computational does not help.

In particular, for the case of the Hamming metric and inputs that have full entropy, our results are as follows.  In  \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.  In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $\log |\mathcal{M}| - \log |B_t(\cdot)|$. Dodis et al. \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08}  construct sketches with essentially the same information-theoretic security\footnote{The security in  \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08}  is expressed in terms of entropy of the error rate; recall that $\log B_t(\cdot)\approx H_q(t/n)$, where $n$ is the number of symbols, $q$ is the alphabet size, and $H_q$ is the $q$-ary entropy function.} . 
In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.

\subsection{Bounds on Secure Sketches using HILL entropy}
\label{sec:imp HILL sketch}
HILL entropy is a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}.  It was extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}. Here we recall a weaker definition due to Gentry and Wichs~\cite{gentry2011separating}~(the term relaxed HILL entropy was introduced in~\cite{reyzin2011some}); since we show impossibility even for this weaker definition, impossibility for the stronger definition follows immediately.

\begin{definition}
\label{def:relaxed hill}
Let $(W, S)$ be a pair of random variables.  $W$ has 
\emph{relaxed HILL entropy} at least $k$ conditioned on $S$,
denoted $H^{\hillrlx}_{\epsilon, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, Y)$, such that $\tilde{H}_\infty(X|Y)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,Y))\leq \epsilon$.
\end{definition}

Intuitively, HILL entropy is as good as average min-entropy for all computationally-bounded observers.  Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the sketch-and-extract construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.  
We will consider secure sketches that retain relaxed HILL entropy: that is, we say that $(\sketch, \rec)$ is a  \emph{HILL-entropy~$(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon,s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\hillrlx}_{\epsilon, s_{sec}}(W|\sketch(W))\geq \tilde{m}$.

Unfortunately, we will show below that such a secure sketch implies an error correcting code with approximately $2^{\tilde{m}}$ points that can correct $t$ random errors (see  \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08} for a similar bound on information-theoretic secure sketches). For the Hamming metric, our result essentially matches the bound on information-theoretic secure sketches of \cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.  In fact, we show that, for the Hamming metric, HILL-entropy secure sketches imply information-theoretic ones with similar parameters, and, therefore, the HILL relaxation gives no advantage.

The intuition for building error-correcting codes from HILL-entropy secure sketches is as follows.  In order to have  $H^{\hillrlx}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $X, Y$ such that $\Hav(X | Y)\geq \tilde{m}$ and $(X, Y)$ is computationally indistinguishable from $(W, \sketch(W))$.  Sample a sketch $s\leftarrow \sketch(W)$. We know that $\sketch$ followed by $\rec$ likely succeeds on $W|s$  (i.e., $\rec (w', s) = w$ with high probability for $w\leftarrow W|s$ and $w'\leftarrow B_t(w)$).  %So, by indistinguishability, it must also succeed on $Y$. 
 Consider the following experiment: 1) sample $y\leftarrow Y$, 2) draw $x\leftarrow X|y$ and 3) $x'\leftarrow B_t(x)$. By indistinguishability, $\rec (x',y) = x$ with high probability.
 This means we can construct a large set $\mathcal{C}$ from the support of $X|y$.  $\mathcal{C}$ will be an error correcting code and $\rec$ an efficient decoder.  We can then use standard arguments to turn this code into an information theoretic sketch.

To make this intuition precise, we need an additional technical condition:  sampling a random neighbor of a point is efficient.
\begin{definition}
\label{def:neighborhood samplable}
We say a metric space $(\mathcal{M}, \dis)$ is $(s_{neigh}, t)$-\emph{neighborhood samplable} if there exists a randomized circuit $\neigh$ of size $s_{neigh}$ that for all $t'\leq t$, $\neigh (w, t')$ outputs a random point at distance $t'$ of $w$.  
\end{definition}

We review the definition of a Shannon code~\cite{shannon1949mathematical}:
\begin{definition}
\label{def:shannon-code}
Let $\mathcal{C}$ be a set over space $\mathcal{M}$.  We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\neigh(c, t')) \neq c]\le \epsilon$. To distinguish it from the average-error Shannon code defined below, we will sometimes call it a \emph{maximal-error} Shannon code.
\end{definition}
This is a slightly stronger formulation than usual, in that for every size  $t'<t$ we require the code to correct $t'$ random errors\footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compared to the volume of the ball of size $t$.  For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.  However, we work with an arbitrary recover functionality that is not necessarily monotone.}.  
Shannon codes work for all codewords. We can also consider a formulation that works for an ``average'' codeword.

 \begin{definition}
Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
$\Pr_{c\leftarrow C}[\rec(\neigh(c, t')) \neq c]\le \epsilon$.
\end{definition}
An average error Shannon code is one whose average probability of error is bounded by $\epsilon$.  See~\cite[Pages 192-194]{cover2006elements} for definitions of average and maximal error probability.  An average-error Shannon code is convertible to a maximal-error Shannon code with a small loss.  We use the following pruning argument from~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
\begin{lemma}
\label{lem:averageToMaximalError}
Let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$ such that $\Hoo(C)\geq k$.  There is a set $\mathcal{C}'$ with $|\mathcal{C}'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
\end{lemma}

We can now formalize the intuition above and show that a sketch that retains $\tilde{m}$-bits of relaxed HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
\begin{theorem}\label{thm:impSketchArbitraryW}
Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  Let $s_{rec}$ denote the size of the circuit that computes $\rec$.  If $s_{sec}\geq (t(s_{neigh}+s_{rec}))$,  then there exists a value $s$ and a set $\mathcal{C}$ with $|\mathcal{C}|\geq 2^{\tilde{m}-2}$  that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
\end{theorem}

>>>>

\ifnum\shownotes=1
\newcommand{\authnote}[2]{{\textcolor{red}{\textsf{#1 notes: }\textcolor{blue}{ #2}}\marginpar{\textcolor{red}{\textbf{!!!!!}}}}}
\else
\newcommand{\authnote}[2]{}
\fi
\newcommand{\bnote}[1]{{\authnote{Ben}{#1}}}
\newcommand{\lnote}[1]{{\authnote{Leo}{#1}}}

@@

\title{Constant Rate Computational Fuzzy Extractors}
\author{Some people}
\begin{document}
\maketitle

%\begin{abstract} 
%We make computational fuzzy extractors better.
%\end{abstract}

\section{Introduction}\label{sec:introduction}
Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} derive stable keys from noisy data.  They are composed of two algorithms: \gen takes a source value $w_0$, and produces a key $r$ and a public value $p$, and \rep which takes a nearby value $w_1$ and $p$ producing the original key $r$.  Intuitively, they are two functions: error correction~(to provide the same value with \emph{noisy} readings) and key derivation~(to transform an entropic source into a uniform key).  Traditionally, these two functions were performed by two separate primitives: a secure sketch~\cite{DBLP:journals/siamcomp/DodisORS08} and a randomness extractor~\cite{nisan1993randomness}.

For a fixed length key, there are two main parameters: the desired error tolerance and the required entropy of the source.  In the information-theoretic setting these two parameter are at odds.  Any increase error-tolerance requires a similar increase to the entropy of the source.  However, this does not need to be the case in the computational setting.  The notion of computational fuzzy extractors was introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.\footnote{The main difference isa computational fuzzy extractor outputs a pseudorandom key instead of a truly random key.  Both definitions appear in \secref{sec:preliminaries}.}  In this setting an error tolerance \emph{larger} than the starting entropy may be possible.  We provide the first construction of a fuzzy extractor where the entropy of the source distribution is smaller than the desired error-tolerance. \footnote{Security is impossible if all points of the source distribution are close together.  In the fuzzy extractor setting, a necessary condition for security is that a negligible portion of the source distribution lies in within the error-tolerance.   This is both a necessary and sufficient condition for security in the interactive setting using two-party computation.}

Our construction is based on obfuscation.  While black-box obfuscation of polynomial time functions is known to be impossible~\cite{barak2001possibility}, we only use the obfuscation of point functions.  This class is known to be achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and generically from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.  Ideally, our construction would be a noisy point obfuscation~(which is a strictly stronger object than a computational fuzzy extractor).  Dodis and Smith constructed noisy point obfuscation when the source entropy is significantly higher than the error-tolerance.  Unfortunately, our construction is not a noisy point obfuscation and leaks partial information about particular blocks of the source.

\section{Preliminaries}
\label{sec:preliminaries}
For a random variable $X = X_1||...|| X_n$ where each $X_i$ is over some alphabet $\mathcal{Z}$, we denote by $X_{1,..., k} = X_1||...|| X_k$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$, 
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.  
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$. 
For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.  We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.
For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t(\cdot)|$ the size of a ball of radius $t$.  We primarily consider the Hamming metric, for two vectors $x, y$ over $\mathcal{Z}^n$ the Hamming distance between $x,y$ is $d(x,y) = \{i | x_i \neq y_i\}$.  For the Hamming metric, $|B_t(\cdot)| = \sum_{i=0}^t {n \choose i} (|\mathcal{Z}|-1)^i $.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
Usually, we use bold letters for vectors or matrices, capitalized letters for random variables, and lowercase letters for elements in a vector or samples from a random variable.

@@

\subsection{Obfuscation}
The standard notion of obfuscation is virtual black-box obfuscation~(introduced by Barak et al.~\cite{barak2001possibility}).  This notion is known to be impossible in a black-box way for all polynomial time programs.  Several variants~(best possible obfuscation~\cite{goldwasser2007best}, indistinguishability obfuscation~\cite{barak2001possibility}, differing inputs indistinguishability obfuscation~\cite{barak2001possibility}) have been presented~(see Varia~\cite{varia2010studies} for implications between various definitions).  Indistinguishability obfuscation has recently been shown to be constructible~\cite{garg2013candidate} using multilinear maps~\cite{garg2013multilinear}.

We present the notion of virtual black-box obfuscation with the weakening that the simulator produces an arbitrarily small $1/\poly$ as all known point obfuscations satisfy this definition.

\begin{definition}~\cite{barak2001possibility, goldwasser2005impossibility}  Let $\mathcal{C}$ be a family of polynomial-size circuits.  A PPT algorithm $\mathcal{O}$ is an obfuscator for $\mathcal{C}$ with dependent auxiliary input if the following conditions are met:
\begin{enumerate}
\item \emph{Approximate Functionality:}  There exists a negligible function $\epsilon$ such that for every $n\in \mathbb{N}$, every circuit $C\in \mathcal{C}_n$, and every $x\in\zo^n$, 
\[
\Pr[\mathcal{O}(C; r)(x) = C(x)] > 1-\epsilon(n),
\]
where the probability is taken over the randomness $r$.  \emph{Almost exact functionality} is a stronger condition that requires $\mathcal{O}(C;r)\equiv C$ with overwhelming probability ver the random coin tosses $r$.  Finally, if this probability always equals $1$, then $\mathcal{O}$ has \emph{exact functionality}.
\item \emph{Polynomial Slowdown:}  There exists a polynomial $\psi$ such that for every $n$, every circuit $C\in \mathcal{C}_n$, and every possible $r$, the circuit $\mathcal{O}(C; r)$ run-in time at most $\psi(n)$.
\item \emph{Virtual Black-box:}  For every PPT adversary $A$ and polynomial $\rho$, there exists a PPT simulator $S$ such that for all sufficiently large $n$, for all $C\in \mathcal{C}_n$, for all auxiliary inputs $z\in \zo^*$, 
and for all binary predicates $\pi$, 
\[
|\Pr[A(\mathcal{O}(C), z) = \pi(C, z)] - \Pr[S^C(1^n, z) = \pi(C, z)] | < \frac{1}{\rho(n)}
\]
where the first probability is taken over the coin tosses of $A$ and $\mathcal{O}$, and the second probability is taken over the coin tosses of $S$.  Furthermore, the.runtime of $A$ and $S$ must be polynomial in the length of their first input.
\end{enumerate}
\end{definition}

In this work, we will use obfuscation of point-programs, 
\[
I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}
\]

We provide the construction of Canetti~\cite{canetti1997towards}, as an illustration of how point functions can be obfuscated.  Let $G$ be a group:
\begin{enumerate}  
\item Input: string $w\in \zo^n$.
\item Choose a generator $g\overset{\$}\leftarrow G$
\item Compute $h\leftarrow g^w$, where $w$ is viewed as an element of $G$ is some canonical way.
\item Output: circuit that has $g, h$ hardwired, and on input $x$, accepts iff $g^x=h$.
\end{enumerate}
\begin{assumption}[Strong DDH assumption]\label{ass:strong ddh}.  Let $n$ be a security parameter and let $p = 2q+1$ be a randomly chosen $n$-bit safe prime.  Consider the group $Q$ of quadratic residues in $\mathbb{F}_p^*$.  For any $W$ with $\Hoo(W)= \omega(\log n)$ where the domain of $W$ is $\mathbb{F}_q$, for $g\overset{\$}\leftarrow Q, a\leftarrow W, b,c \overset{\$}\leftarrow \mathbb{F}_q$, the ensembles $\langle g, g^a, g^b, g^{ab}\rangle$ and $\langle g, g^a, g^b, g^c\angle$ are computationally indistinguishable.
\end{assumption}
\begin{theorem}~\cite{canetti1997towards}
The construction above, when instantiated with the group $G = Q$ is a virtual black-box obfuscator for the family of point functions under \assref{ass:strong ddh}.
\end{theorem}

As described above there exist other constructions of point function obfuscates under various assumptions~\cite{lynn2004positive, wee2005obfuscating}.

Lastly, we will need the notion of composable obfuscation.

\begin{definition}[Composable obfuscation~\cite{bitansky2010strong, canetti2008obfuscating,lynn2004positive}].  A PPT algorithm $\mathcal{O}$ is a $t$-\emph{com posable obfuscator} for the family $\mathcal{C}$ with dependent auxiliary input if functionality and polynomial slowdown hold as before, and the virtual black black-box property holds whenever the adversary and simulator are given up to $t$ circuits in $\mathcal{C}$.  That is, for every PPT $A$ and polynomial $\rho$, there exists a PPT $S$ such that for all sufficiently large $n$, and for all $C_1,..., C_t\in \mathcal{C}_n$, and for all auxiliary inputs $z\in \zo^*$, 
\[
|\Pr[A(\mathcal{O}(C_1), ..., \mathcal{O}(C_t), z) = 1] - \Pr[S^{C_1,..., C_t}(1^n, z) = 1]| < \frac{1}{\rho(n)},
\]
where the probabilities are taken over the random coins tosses of $A, S$ and $\mathcal{O}$.  The runtimes of $A$ and $S$ must be polynomial in the length of their first input.
\end{definition}

\section{Supported Sources}
We now describe a set of high entropy sources appropriate for our construction.  After giving the description of the distribution, we give examples of distributions that fit in this class and provide additional characterizations.

\begin{definition}
Let $\mathcal{O}_{w_1,..., w_k}$ be an oracle that return $\mathcal{O}_{w_1,..., w_k}(i, w_i')=\left( w_i\overset{?}=w_i'\right)$.
A source $W = W_1||...|W_k$ is a $(q, \alpha, \ell)$-\emph{guessable block distribution} if for any adversary $A$~(not bounded in time or space) with oracle access to $\mathcal{O}$ making at most $q$ queries there exists a set $S$ of size at least $\ell$ such that 
\[
\forall i\in S, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}
This type of source seems to be inherently adaptive and is difficult to formulate in a clean information-theoretic notion.  However, we can show necessary and sufficient types of sources for a guessable block distribution.  We begin by defining the entropy jump of a block source which will appear in our characterization.

\begin{definition}
Let $W = W_1,..., W_k$ be a source under ordering $i_1,..., i_k$.  The \emph{entropy jump} of a block $i_j$ is $J(i_j) = \Hav(W_{i_j} | W_{i_1},..., W_{i_{j-1}})$.
\end{definition}

\begin{claim}
Let $W$ be a $(q, \alpha, \ell)$-guessable block distribution.  Then for all orderings $i_1, ...., i_k$ there is some $j\leq k-\ell$ such that $J(i_j)> \log q + \alpha$.
\end{claim}
\begin{proof}
Suppose not, for convenience assume the ordering that violates this condition is $1,..., k$.  We describe a distribution $W$ where $\forall 1\leq j\leq k-\ell$, $J(j)\leq \log q +\alpha$. Define $W$ as follows $W_1 = c_1,...., W_{j-1} = c_{j-1}$ are constants.
\end{proof}
\bibliographystyle{alpha}
\bibliography{crypto}

\end{document}
